%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Vice President of Engineering \& Chief Platform Architect}
{Olive AI}
{Austin, TX}
{Nov. 2021 - Present}
{
  \begin{cvitems}
    \item{Invested in initiatives to improve engineering cultural values of curiosity, continuous learning, data-oriented decision making}
    \item{Worked to raise developer quality bar by creating a consistent competencies framework and interview process}
    \item{Created and disseminated Olive platform vision and strategy}
    \item{Scaled event-driven architecture broadly across multiple engineering teams. Sponsored aditional research efforts in graph data, machine learning, and data protection}
    \item{Guided teams in creation of architecture and development standards}
    \item{Managed a 110 person engineering organization. Responsible for organizational design, communications, performance management, leader coaching, and resource planning}
  \end{cvitems}
}
    
%------------------------------------------------

\cventry
{VP Engineering, Olive Assures}
{Olive AI}
{Austin, TX}
{Jan. 2021 - Nov. 2021}
{
  \begin{cvitems}
    \item {Defined technical strategy for new predictive analytics product}
    \item {Partnered with product management and executive leadership to ensure that engineering efforts align with business objectives}
    \item {Delivered a new software service to two beta customers and processed > 1MM USD within the first 6 months of operation}
    \item {Built a remote-first, cross-disciplinary team of 20 from nothing in 6 months}
  \end{cvitems}
}

%------------------------------------------------

\cventry
{Principal Software Architect}
{SAP}
{Austin, TX}
{Mar. 2020 - Dec. 2020}
{
  \begin{cvitems}
  \item {Drove data and analytics workstream across all SAP application businesses}
  \item {Partnered with both central engineering organizations and CTO offices in order to drive consensus on tools and architectural approaches across the company}
  \item {Envisioned, prototyped, and evangelized a future-state architecture for integrating applications across SAP businesses, partners, and customers}
  \item {Researched and prototyped a lightweight OWL reasoning engine and its application in a variety of different transactional workloads}
  \item {Advised multiple cross-business unit integration projects. Create and evangelize architecture concept, participate in design reviews, and resolve conflicts as they arise}
  \end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Director of Software Development}
{SAP Concur}
{Bellevue, WA}
{Dec. 2018 - Mar. 2020}
{
  \begin{cvitems}
  \item {Partnered with SAP central engineering to drive cross-company technology initiatives into Concur delivery teams as well as influence the strategies of those groups}
  \item {Created technology vision and strategy by working across central technology organizations as well as over 80 delivery teams to understand both the business domain and non-functional constraints. Produced both multi-year vision and iterative strategies for realizing the vision}
  \item {Managed a globally distributed team of 13 architects and senior developers across North America and Europe}
  \item {Researched semantic technologies, including RDF, OWL, and SPARQL, as well as the application of semantic technologies to event-driven, cloud-native architecture}
  \item {Led global architecture for the SAP Concur’s spend management product. Partnered with delivery teams on short term tactical challenges and executive leadership on long term technology strategy}
  \item {Identified key measures for driving consistent quality of service and return on investment across the service portfolio}
  \item {Gave multiple presentations within SAP, focused primarily on application of semantic technologies to business software}
  \end{cvitems}
}

%------------------------------------------------    

\cventry
{Director of Software Development}
{SAP Concur}
{Bellevue, WA}
{Jun. 2015 - Dec. 2018}
{
  \begin{cvitems}
  \item {Distilled high-level executive management goals into concrete problem definitions to be pursued by both my development teams and business counterparts}
  \item {Manageed a team of 25 developers (including 3 development managers), divided into 3 organizational units. Included employees in Bellevue, WA, Vienna, VA, and Maidenhead UK}
  \item {Partnered with colleagues in France and Japan to deliver next generation receipts service globally}
  \item {Coordinated with colleagues in Germany and Prague to deliver a data orchestration service}
  \item {Helped to create career competencies and paths for all Concur engineers and managers}
  \item {Participated in physical space design/planning to create a collaborative team environment}
  \item {Created mock interview program in partnership with \href{https://www.codefellows.org/}{Code Fellows} and integrated it into our organization’s interview training program}
  \item {Actively managed relationships with peers across the company for building consensus around key company-level decisions}
  \item {Conducted competitive analyses and presented 5-year strategic plan to company executives}
  \item {Spoke at SAP global developer conference in Germany two years in a row. Highest-rated lecturer by external company in 2016}
  \item {Managed budgets for personnel, morale, and equipment}
  \end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Manager Software Development}
{SAP Concur}
{Bellevue, WA}
{Sept. 2014 – Jun. 2015}
{}

%------------------------------------------------

\cventry 
{Senior Program Manager (ASP.NET)}
{Microsoft Corporation}
{Redmond, WA}
{Jan. 2012 – Sept. 2014}
{}

%------------------------------------------------

\cventry 
{Program Manager II (AppFabric Developer Platform)}
{Microsoft Corporation}
{Redmond, WA}
{Jan. 2011 – Jan. 2012}
{}

%------------------------------------------------

\cventry 
{Program Manager II (Server and Tools Online)}
{Microsoft Corporation}
{Redmond, WA}
{Sept. 2009 – Jan. 2011}
{}

%------------------------------------------------

\cventry
{MSDN Magazine, Editor-in-Chief}
{Microsoft Corporation}
{Redmond, WA}
{Jul. 2007 – Sept. 2009}
{}

%------------------------------------------------

\cventry 
{Microsoft Learning, Certification Product Planner}
{Microsoft Corporation}
{Redmond, WA}
{Jul. 2006 – Jul. 2007}
{}

%------------------------------------------------

\cventry 
{Managing Consultant, Technical Project Lead (AIG)}
{Software Architects, Inc.}
{Houston, TX}
{Aug. 2005 – Jun. 2006}
{}

%------------------------------------------------

\cventry 
{Lead Architect (Aramco Services Company)}
{Riversand Technologies}
{Houston, TX}
{Nov 2004 – Jul 2005}
{}

%------------------------------------------------

\cventry 
{Senior Systems Architect}
{Riversand Technologies}
{Houston, TX}
{Jun. 2004 – Nov. 2004}
{}

%------------------------------------------------

\cventry 
{eCo Technical Architect/Team Lead (Hewlett-Packard)}
{Riversand Technologies}
{Houston, TX}
{Sept. 2003 – Jun. 2004}
{}

%------------------------------------------------

\cventry 
{Senior Programmer/Analyst}
{AMSI}
{Houston, TX}
{Dec. 1999 – Sept. 2003}
{}

%------------------------------------------------

\end{cventries}