% TODOs for my own template
% * have a summary section for each role preceding the bulleted list of competencies
% * consider separating competencies from the cvitem description in the bullet - maybe they could be more like tags?
% * formalize professional transition
% * formalize competencies
%   Organizational Leadership
%   Vision Development
%   Technology Research and Strategy
%   Architecture
%   Team Management
%   Business Strategy
%   Public Speaking
%   Teaching and Writing
%   Open Source
%   Global Project Management
%   Stakeholder Engagement
%   Budget Management
%   Product Planning
%   Vision Development \& Technology Research and Strategy
%   Vision Development \& Organizational Leadership
%   Technology Research and Strategy \& Architecture
%   Vision Development \& Product Planning
%   Product Planning \& Business Strategy
% * look into whether tex can iterate "first n" cventries for full descriptions and then put just titles for everything else (for resume only)





%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Vice President of Engineering \& Chief Platform Architect}
{Olive AI}
{Austin, TX}
{Nov. 2021 - Apr. 2023}
{
  \begin{cvitems}
    \item{\emph{Organizational Leadership:} Senior leader within a roughly 350 person engineering organization. Focus on engineering culture - curiosity, continuous learning, data-oriented decision-making - and bar raising via development of consistent competencies framework and interviewing practices.}
    \item{\emph{Vision Development:} Created and disseminated Olive platform vision and strategy}
    \item{\emph{Technology Research and Strategy:} Scaled neuron architecture broadly across multiple engineering teams. Funded additional research efforts in graph data, machine learning, and data protection. }
    \item{\emph{Architecture:} Designed neuron architecture to allow for rapid, distributed development while still enabling integrated data. Led team in creation of architecture and development standards. }
    \item{\emph{Team Management:} Manage a 110-person engineering organization. Responsible for organizational design, communications, performance management, leader coaching, and resource planning.}
  \end{cvitems}
}

%------------------------------------------------

\cventry
{Vice President of Engineering}
{Olive AI}
{Austin, TX}
{Jan. 2021 - Nov. 2021}
{
  \begin{cvitems}
    \item{\emph{Organizational Leadership:} Executive team member for a new business venture (P\&L) within the larger corporation. Helped to form and execute operating cadence, both within our organization and with corporate executive management. }
    \item{\emph{Technology Research and Strategy:} Created lightweight RDFS reasoner that can be used in a JavaScript lambda function. }
    \item{\emph{Architecture:} Designed, created a proof of concept reference implementation, and socialized a novel distributed architecture combining event-driven architecture, serverless computing, and RDF ("neuron architecture"). }
    \item{\emph{Team Management:} Built a highly capable engineering team from the ground up - from zero to 15 in 6 months. }
    \item{\emph{Business Strategy:} As part of the executive team for a P\&L, worked to craft and review strategy for product, monetization, and go-to-market. }
    \item{\emph{Stakeholder Engagement:} Worked across other P\&Ls as well as the corporate executive team to drive consensus around technology strategy. Worked with pilot customers to identify and refine product capabilities. }
    \item{\emph{Professional Transition:} Promoted to Senior Vice President of Engineering \& Chief Platform Architect as part of a larger company reorganization }
  \end{cvitems}
}

%------------------------------------------------

\cventry
{Principal Software Architect}
{SAP}
{Austin, TX}
{Mar. 2020 - Present}
{
  \begin{cvitems}
  \item {\emph{Organizational Leadership:} Responsible for driving data and analytics work stream across all SAP application businesses. Partner with both central engineering organizations and CTO offices in order to drive consensus on tools and architectural approaches across the company }
  \item {\emph{Vision Development:} Envision, prototype, and evangelize a future-state architecture for integrating applications across SAP businesses, partners, and customers.}
  \item {\emph{Technology Research and Strategy:} Current research is centered around the development of a lightweight OWL reasoning engine and its application a variety of different transactional workloads }
  \item {\emph{Architecture:} Advise multiple cross-business unit integration projects. Create and evangelize architecture concept, participate in design reviews, and resolve conflicts as they arise }
  \item{\emph{Professional Transition:} Pursued opportunity outside of SAP}
  \end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Director of Software Development} % Job title
{SAP Concur} % Organization
{Bellevue, WA} % Location
{Dec. 2018 - Mar. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Organizational Leadership:} Partnered with SAP central engineering to drive cross-company technology initiatives into Concur delivery teams as well as influenced the strategies of those groups }
\item {\emph{Vision Development:} Created technology vision and strategy by working across central technology organizations as well as over 80 delivery teams to understand both the business domain and non-functional constraints. Produced both multi-year vision and iterative strategies for realizing the vision }
\item {\emph{Team Management:} Managed a globally distributed team of 13 architects and senior developers across North America and Europe }
\item {\emph{Technology Research and Strategy:} Focused research on semantic technologies, including RDF, OWL, and SPARQL, as well as the application of semantic technologies to event-driven, cloud-native architecture }
\item {\emph{Architecture:} Head of global architecture for the SAP Concur spend management product. Partnered with delivery teams on short term tactical challenges and executive leadership on long term technology strategy }
\item {\emph{Business Strategy:} Identified key measures for driving consistent quality of service and return on investment across the service portfolio }
\item {\emph{Public Speaking:} Lecturer within SAP, focused primarily on the application of semantic technologies to business software }
\item {\emph{Teaching and Writing:} Published Pluralsight course on Google Cloud Platform as well as continued blogging }
\item {\emph{Open Source:} Released tool to produce static documentation Website from a semantic vocabulary }
\item {\emph{Professional Transition:} Moved from Concur to SAP Central Architecture team }
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Director of Software Development} % Job title
{SAP Concur} % Organization
{Bellevue, WA} % Location
{Jun. 2015 - Dec. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Vision Development:} Distilled high-level executive management goals into concrete problem definitions that could be pursued by both my development teams and our business counterparts }
\item {\emph{Team Management:} Managed a team of 25 developers (including 3 development managers), divided into 3 organizational units. Included employees in Bellevue, WA, Vienna, VA, and Maidenhead UK }
\item {\emph{Global Project Management:} Partnered with colleagues in France and Japan to deliver next generation receipts service globally. Coordinated with colleagues in Germany and Prague to deliver a data orchestration service. Actively oversaw the development and operation of 5 projects in various stages of development }
\item {\emph{Organizational Leadership:} Worked to create career competencies and paths for all Concur engineers and managers. Participated in physical space design/planning to create a collaborative team environment. Participated in additional cross-company functions as part of the CTO extended leadership group. Influenced technical leaders across SAP in areas such as service design and architecture. Created a mock interview program in partnership with \href{https://www.codefellows.org/}{Code Fellows} and integrated it into our interview training program }
\item {\emph{Stakeholder Engagement:} Actively managed relationships with peers across the company for building consensus around key company-level decisions. Participated in partner engagements to ensure that customer requirements were clearly understood and that partners felt supported }
\item {\emph{Business Strategy:} Conducted competitive analyses and presented 5-year strategic plan to company executives }
\item {\emph{Technology Research and Strategy:} Actively researched and provided thought leadership for semantic web and linked data technology as well as cloud-native software architecture }
\item {\emph{Public Speaking:} Invited to speak at SAP developer conference in Germany two years in a row. Highest-rated lecturer by external company in 2016 }
\item {\emph{Budget Management:} Managed budgets for personnel, morale, and equipment }
\item {\emph{Professional Transition:} Promoted to Senior Director }
\end{cvitems}
}

%------------------------------------------------


\cventry
{Senior Manager Software Development}
{SAP Concur}
{Bellevue, WA}
{Sept. 2014 – Jun. 2015}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Team Management:} Led a team of 5 Concur developers to build a variety of online service offerings to improve the adoption of the Concur platform }
\item {\emph{Global Project Management:} Drove delivery for 3 Concur products, including the \href{https://developer.concur.com}{Concur developer center}, client libraries (\href{https://www.npmjs.com/package/concur}{NPM}, \href{https://www.nuget.org/packages/ConcurPlatform/}{NuGet}), and the highly-publicized \href{http://www.bloomberg.com/news/videos/2015-02-23/concur-taking-the-pain-out-of-expense-reports}{Starbucks connector} }
\item {\emph{Product Planning:} Captured business scenarios for the Concur/Starbucks partnership and set up the basic structure and vision for the team to execute on }
\item {\emph{Vision Development \& Technology Research and Strategy:} Spearheaded microservices architecture efforts using the Amazon Web Services (AWS) public cloud. Delivered Starbucks connector application to production in 3 months with a team of 3 people. Designed technology and strategies for converting Concur developer center from a traditional content management system model to a statically-generated website with content authored in Markdown and managed on GitHub }
\item {\emph{Public Speaking:} Gave multiple presentations (both within and outside the company) on services architecture, developer pipeline, and team workflow }
\item {\emph{Open Source:} Drove release of multiple team projects as \href{https://github.com/concur}{open-source on GitHub}, including the Concur developer center. Since release as open source, developer center has been forked 50+ times and has 50+ contributors }
\item {\emph{Professional Transition:} Promoted to Director }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Principal}
{Dierking Consulting, LLC}
{Redmond, WA - Austin, TX}
{Apr. 2013 – Present}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Dierking Consulting is a company that I formed in order to apply personal research topics to real-world scenarios and customers }
\item {\emph{Technology Research and Strategy:} Research tools and techniques for building large-scale, cloud-native applications. Topics gravitate around cloud platforms and data management/processing tools }
\item {\emph{Architecture:} Help customers define and create software systems for a variety of different business domains and technology stacks. Have worked with companies of all types and sizes (including a large health insurance company, a child safety non-profit, and a 3-person Silicon Valley startup) }
\item {\emph{Global Project Management:} Led client development teams in the United States, Mexico, Europe, and Asia in implementing designs and delivering capabilities }
\item {\emph{Business Strategy:} Performed market analyses for clients to determine product and feature viability. Participated in go-to-market strategy creation and execution }
\item {\emph{Teaching and Writing:} Created online training material for Pluralsight, contributed to several books and journals, and regularly publish content on \href{https://www.howarddierking.com}{personal Web site} }
\item {\emph{Professional Transition:} Ongoing, as time permits }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Senior Program Manager (ASP.NET)}
{Microsoft Corporation}
{Redmond, WA}
{Jan. 2012 – Sept. 2014}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Global Project Management:} Project owner for the NuGet package management system, ASP.NET Web-optimization code library, and the “Katana Project” runtime. Managed project rhythm and delivery schedule for both internal and external customers. Delivered multiple versions of all projects including introducing the debut version of the Katana project to Microsoft customers }
\item {\emph{Open Source:}  Assumed management of open source projects for \href{https://github.com/NuGet}{NuGet}. Created a new open-source community for the Katana project (later became \href{https://github.com/aspnet/GetStarted}{next generation ASP.NET}, and drove the open sourcing of the core ASP.NET Web Optimization framework }
\item {\emph{Public Speaking:} Represented my teams and Microsoft at internal and external industry events. Provided in-depth lectures and consulting to Microsoft customers. Recorded video lectures as a part of product launch collateral }
\item {\emph{Teaching and Writing:} Authored numerous journal articles in support of my teams and projects. Authored and reviewed official product documentation }
\item {\emph{Technology Research and Strategy:} Built applications in competing technology stacks to understand trade offs in developer experience, and then distilled findings into feature design. Directly applied expertise in RESTful systems to the \href{https://docs.nuget.org/ndocs/api/nuget-api-v3}{design of a new NuGet server} }
\item {\emph{Stakeholder Engagement:} Maintained critical partnerships with many internal teams across divisions in order to deliver projects on time. Drove creation of partnership between NuGet and Sonatype which resulted in a new NuGet feature (package license discovery) with almost zero engineering investment }
\item {\emph{Vision Development \& Organizational Leadership:} Drove efforts to apply NuGet and package management for changing core development processes inside Microsoft. Worked across divisions to design and promote significant tooling improvements to support package management workflows }
\item {\emph{Professional Transition:} Decided to \href{https://www.howarddierking.com/2014/08/14/leaving-microsoft/}{pursue new opportunities outside of Microsoft} }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Program Manager II (AppFabric Developer Platform)}
{Microsoft Corporation}
{Redmond, WA}
{Jan. 2011 – Jan. 2012}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Global Project Management:} Drove milestone planning and ran regular bug triage with development and test counterparts. Represented team in organizational tactics and ship room meetings to ensure that risks and dependencies were properly communicated across the organization }
\item {\emph{Technology Research and Strategy:} Researched industry-standard specifications, practices, and tools to create proposals and specifications for the WCF Web API service framework. Authored sample code which was included as a part of the Windows SDK }
\item {\emph{Stakeholder Engagement:} Partnered with 4 key Microsoft product teams representing both dependencies and dependents to ensure that all teams were not blocked }
\item {\emph{Public Speaking:} Represented team and Microsoft at large industry conferences, \href{https://channel9.msdn.com/Events/TechEd/NorthAmerica/2011/MID307}{including Microsoft TechEd}. Met with several enterprise Microsoft customers to evangelize the new framework and consult on a migration path }
\item {\emph{Teaching and Writing:} Published in industry journals to evangelize and educate on the Web API service framework }
\item {\emph{Professional Transition:} Reorganized into ASP.NET team and promoted }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Program Manager II (Server and Tools Online)}
{Microsoft Corporation}
{Redmond, WA}
{Sept. 2009 – Jan. 2011}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Team Management:} Drove a cross-disciplinary, 5-person team to select, customize, and deploy an open source content management system (CMS) in a multi-datacenter architecture for \href{https://msdn.microsoft.com}{MSDN} and \href{https://technet.microsoft.com}{TechNet} }
\item {\emph{Technology Research and Strategy \& Architecture:} Investigated internal details of \href{https://umbraco.com}{Umbraco CMS} to create feature designs and implement best practices for development and operations teams. Sought out by development teams to review technical architecture/feature code }
\item {\emph{Stakeholder Engagement:} Gathered and validated requirements from content teams across all of Microsoft who would need to manage content on new CMS. Worked closely with Microsoft network operations and security teams to ensure that CMS was delivered in a highly scalable and secure manner }
\item {\emph{Organizational Leadership:} Drove the CMS development team to adopt agile tools such as distributed version control and practices such as continuous integration and delivery. This enabled the CMS team to deliver improvements rapidly (sometimes multiple times per day) }
\item {\emph{Open Source:} Worked closely with the Umbraco core team to deliver content management implementation (including reporting feature gaps and issues to the leadership team to improve the open-source product) }
\item {\emph{Professional Transition:} Resigned in pursuit of product team experience }
\end{cvitems}
}

%------------------------------------------------

\cventry
{MSDN Magazine, Editor-in-Chief}
{Microsoft Corporation}
{Redmond, WA}
{Jul. 2007 – Sept. 2009}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Vision Development \& Product Planning:} Drove content strategy and editorial direction for MSDN Magazine (both print and online assets) }
\item {\emph{Global Project Management:} Ensured that 24+ issues of the magazine consistently released on time to both the printer and the website }
\item {\emph{Stakeholder Engagement:} Partnered with various business and product marketing organizations (e.g. MS Office and Visual Studio teams) as well as with engineering teams to build consensus around editorial strategy as well as secure authors and technical reviewers }
\item {\emph{Team Management:} Managed a team of 2 Microsoft FTEs and 3 vendors }
\item {\emph{Budget Management:} Managed an annual acquisitions budget of 300,000 USD }
\item {\emph{Organizational Leadership:} Built process automation and business intelligence solutions using SharePoint and the SQL Server BI stack to streamline editorial and production process (as well as improve the decision-making process around investments) }
\item {\emph{Technology Research and Strategy:} Designed, developed, and released MSDN Magazine Pivot viewer, as well as the source code }
\item {\emph{Teaching and Writing:} Authored monthly editor’s note with commentary and insights on the current issue’s theme and content }
\item {\emph{Public Speaking:} Represented the magazine at many large industry events (e.g. TechEd, TechEd Europe, DevConnections) }
\item {\emph{Professional Transition:} Was reorganized into the Server and Tools Online group }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Microsoft Learning, Certification Product Planner}
{Microsoft Corporation}
{Redmond, WA}
{Jul. 2006 – Jul. 2007}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Product Planning \& Business Strategy:} Determined the most impactful strategies for MSL investments in developer certification exams }
\item {\emph{Stakeholder Engagement:} Worked with Microsoft product and business groups to build consensus on exam portfolio strategy and secured additional funding where needed. Worked with Microsoft business partners to create new technology solutions to support the certification business }
\item {\emph{Global Project Management:} Supported exam development process as a technology expert. Worked across Microsoft Learning business units to ensure that exams had supporting training material }
\item {\emph{Vision Development:} Worked with MSL product development group to create new models for exam creation using techniques such as crowdsourcing and machine learning }
\item {\emph{Technology Research and Strategy:} Created tools to automate redundant data processing tasks for exam creation. Filed patent for automated matching of employers and potential employees using machine learning and certification data }
\item {\emph{Professional Transition:} Pursued MSDN Magazine Editor-in-Chief Position }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Managing Consultant, Technical Project Lead (AIG)}
{Software Architects, Inc.}
{Houston, TX}
{Aug. 2005 – Jun. 2006}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Technology Research and Strategy \& Architecture:} Designed and constructed metadata-based architecture which enabled distributed work streams based on various insurance products and reuse of code assets across those work streams. Product architecture reduced new product introduction time by at least 50\% }
\item {\emph{Team Management:} Led team of 3 consultants and 4 AIG employees in design and implementation of a web-based insurance products application for 40,000 insurance agents }
\item {\emph{Organizational Leadership:} Drove an agile life cycle management strategy utilizing Microsoft Visual Studio 2005 Team System }
\item {\emph{Teaching and Writing:} Became subject-matter expert for creating and reviewing Microsoft developer certification exams. Author for Exam 70-529 (Distributed Application Development) }
\item {\emph{Professional Transition:} Was recruited by Microsoft to run the team for whom I was a subject-matter expert }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Lead Architect (Aramco Services Company)}
{Riversand Technologies}
{Houston, TX}
{Nov 2004 – Jul 2005}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Team Management:} Led team of 3 Aramco employees in a variety of internal software development projects that leveraged object-oriented design, .Net implementation, and project life cycle management }
\item {\emph{Architecture:} Designed web-based finance management tool which was responsible for accurately calculating and tracking purchases and sales of crude oil (approximately 600 MM USD per month). Designed budgeting and planning application which provided data entry and roll-up capabilities for budget representatives at various levels of the organization and generated executive management reports for strategic decision-making }
\item {\emph{Global Project Management:} Worked across multiple organizations, both technical and business, to deliver 2 internal finance applications }
\item {\emph{Stakeholder Engagement:} Gathered and validated requirements with business stakeholders. Ensured business sign-off for multiple, agile releases }
\item {\emph{Organizational Leadership:} Introduced agile development practices to the larger development organization, including continuous integration, test-driven development, and automated deployment }
\item {\emph{Professional Transition:} Though I was in the consulting part of the business, Riversand’s primary focus was its product. I wanted more consulting experience, so I left to join a consulting firm }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Senior Systems Architect}
{Riversand Technologies}
{Houston, TX}
{Jun. 2004 – Nov. 2004}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Organizational Leadership:} Designed and implemented an agile software development process used to coordinate parallel work of both U.S. and India development and QA teams }
\item {\emph{Technology Research and Strategy:} Created automated build process which included unit test runs }
\item {\emph{Global Project Management:} Coordinated work between development teams in the United States and test teams in India }
\item {\emph{Professional Transition:} Believed that I would be able to have a more profound impact by moving back to the consulting side of the business }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{eCo Technical Architect/Team Lead (Hewlett-Packard)}
{Riversand Technologies}
{Houston, TX}
{Sept. 2003 – Jun. 2004}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Architecture:} Worked in developing a new technical application architecture for all product configuration applications for the Quote \& Config organization. Designed application architecture for a web-based data mart reporting tool }
\item {\emph{Global Project Management (Quote \& Config):} Led a team of contractors and HP employees based in Houston, Palo Alto, and Germany in the implementation of a new .NET web-based configuration application – delivered application 3 months ahead of schedule }
\item {\emph{Global Project Management (Knowledge Point Express):} Guided a junior consultant in turning around what had been a failing project and delivered the working application within 3 months of taking over the development effort }
\item {\emph{Organizational Leadership:} Provided technical best practices and guidance to HP's Quote \& Config development group. Modified existing development processes to include daily, automated builds }
\item {\emph{Professional Transition:} Wanted to shift focus to product-oriented work }
\end{cvitems}
}

%------------------------------------------------

\cventry 
{Senior Programmer/Analyst}
{AMSI}
{Houston, TX}
{Dec. 1999 – Sept. 2003}
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\emph{Technology Research and Strategy:} Built application features for multiple products in AMSI’s product portfolio using Visual Basic 6 and ASP. Investigated and created strategy for developing web-based applications using Visual Basic rather than classic ASP scripts. Created technology components and strategy for rendering web application components from within the browser while interacting with data from a server (this approach was later referred to as “AJAX”) }
\item {\emph{Architecture:} Designed and developed .NET web application architecture to provide unified support for exception handling, error reporting, tracing, data access, configuration, and encryption }
\item {\emph{Organizational Leadership:} Designed and implemented a source control strategy and build automation strategy. Represented AMSI engineering group to senior management when the company was acquired by Infor }
\item {\emph{Professional Transition:} After the acquisition, I wanted to seek out new professional experiences }
\end{cvitems}
}

%------------------------------------------------

\end{cventries}