%----------------------------------------------------------------------------------------
% SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Open Source Contribution}

%----------------------------------------------------------------------------------------
% SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{\url{https://github.com/howarddierking/metalsmith-ldschema}}  % link
{metalsmith-ldschema}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  Metalsmith plugin for generating Web documentation for a linked data vocabulary. Inspired by https://schema.org.
}

%------------------------------------------------

\cventry
{\url{https://github.com/howarddierking/blog.howarddierking.com}}  % link
{www.howarddierking.com}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  My personal blog. Also a testbed for experiments with different Node-based static site generators.
}

%------------------------------------------------

\cventry
{\url{https://github.com/howarddierking/building-restful-services}}  % link
{building-restful-services}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  Contains all sample code for my Pluralsight course, Building RESTful Services.
}

%------------------------------------------------

\cventry
{\url{https://github.com/howarddierking/international-address}}  % link
{international-address}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  NodeJS-based formatting library for international addresses.
}

%------------------------------------------------

\cventry
{\url{https://bitbucket.org/howarddierking/ssis-wcf-dataservices}}  % link
{ssis-wcf-dataservices}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  This code sample shows you how to create a SQL Server Integration Services custom data source that can interoperate with WCF Data Services (formerly known as Astoria). In addition to simply illustrating the mechanics of working with SSIS and ADO.NET Data Services, the sample also illustrates some design practices and techniques such as separation of concerns and behavior-driven development.
}

%------------------------------------------------

\cventry
{\url{https://bitbucket.org/howarddierking/msdnmagpivot-public}}  % link
{msdnmagpivot-public}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  Source code used to create and display the MSDN Magazine collection for the Silverlight Pivot viewer control.
}

%------------------------------------------------

\cventry
{\url{https://github.com/howarddierking/RestBugs}}  % link
{RestBugs}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  A simple, hypermedia-driven bug tracking API.
}

%------------------------------------------------

\cventry
{\url{https://github.com/nuget}}  % link
{NuGet}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  NuGet is the package manager for the Microsoft development platforms including .NET. Create, share, and reuse thousands of NuGet packages.
}

%------------------------------------------------

\cventry
{\url{https://github.com/aspnet}}  % link
{ASP.NET}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  ASP.NET is an open source web framework for building modern web apps and services with .NET. ASP.NET creates websites based on HTML5, CSS, and JavaScript that are simple, fast, and can scale to millions of users.
}

%------------------------------------------------

\cventry
{\url{https://aspnetoptimization.codeplex.com/}}  % link
{Web Optimization}  % project name
{\enskip} % ?
{\enskip} % ?
{
  % Description(s)
  The ASP.NET Web optimization framework provides services to improve the performance of your ASP.NET Web applications.
}

\end{cventries}